Validation of marker gene expression

### 2025-02-26 analyses/cell-type-consensus/template-notebooks/marker-gene-validation.Rmd
make note about keeping HPCs

First we will look at the expression of marker genes that are specific to a cell type group.  
All marker genes shown in the following plots are only found to be a marker gene for a single cell type group. 
Only cell type groups with at least 50 cells will be shown.

>>>>

First we will look at the expression of marker genes that are specific to a cell type group.  
All marker genes shown in the following plots are only found to be a marker gene for a single cell type group with the exception of marker genes for hematopoietic precursor cells, as none of those genes are unique to a single cell type and may also be found in other immune cells.
Only cell type groups with at least 50 cells will be shown.
